{ \centering Scientific Report - Summary of Research\\ ~\\ ``Automatized compilation of sequential software to a diverse set of hardware accelerators''\\ } ~\\ \vspace{18em} \large Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
deploy: 0c2d39d9b19dba8d8383e366560053e5a097a585

%% Title information
\title[]{
	{
	\centering
	Scientific Report - Summary of Research\\
	~\\
Automatized compilation of sequential software to a diverse set of
hardware accelerators\\
}
~\\
\vspace{18em}
\large
Grant number: PZ00P2 168016\\
Period: 01.05.2018– 31.12.2020\\
Grantee: Tobias Grosser\\
\today
}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.

>>>>

%% Title information
\title[]{
	{
	\centering
	Scientific Report - Summary of Research\\
	~\\
``Automatized compilation of sequential software to a diverse set of
hardware accelerators''\\
}
~\\
\vspace{18em}
\large
Grant number: PZ00P2 168016\\
Period: 01.05.2018– 31.12.2020\\
Grantee: Tobias Grosser\\
\today
}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
